%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% A clean template for an academic CV. This is a short summary version.
%
% Uses tabularx to create two column entries (date and job/edu/citation).
% Defines commands to make adding entries simpler.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[10pt, letterpaper]{article}

% Full Unicode support for non-ASCII characters
\usepackage[utf8]{inputenc}

% Useful aliases
\newcommand{\WHOI}{Woods Hole Oceanographic Institution}
\newcommand{\WUSTL}{Washington University in St Louis}
\newcommand{\UChi}{University of Chicago}
\newcommand{\JP}{MIT-WHOI Joint Program}
\newcommand{\MIT}{Massachusetts Institute of Technology}
\newcommand{\mathrev}{WHOI Summer Math Review}
\newcommand{\AGU}{AGU Fall Meeting}
\newcommand{\gull}{Gull Island Institute}
\newcommand{\LDEO}{Lamont-Doherty Earth Observatory}
\newcommand{\CU}{Columbia University}

% Identifying information
\newcommand{\Title}{Curriculum Vit\ae}
\newcommand{\FirstName}{Hannah}
\newcommand{\LastName}{Mark}
\newcommand{\MiddleName}{F.}
\newcommand{\MyName}{Dr. \FirstName\ \MiddleName\ \LastName}
\newcommand{\Initials}{HF}  % for citations in particular
\newcommand{\Me}{\textbf{\LastName, \Initials}}  % For citations
\newcommand{\Email}{hmark@ldeo.columbia.edu}
\newcommand{\PersonalWebsite}{hfmark.github.io}
%\newcommand{\LabWebsite}{www.compgeolab.org}
\newcommand{\ORCID}{0000-0002-1722-3759}
\newcommand{\Address}{
  266 Woods Hole Road MS\#24, Woods Hole, MA, 02543
}

% Names for citing coauthors
\newcommand{\Josh}{Russell, JB}
\newcommand{\Jim}{Gaherty, JB}
\newcommand{\Greg}{Hirth, G}
\newcommand{\LHans}{Hansen, LN}
\newcommand{\danl}{Lizarralde, D}
\newcommand{\jac}{Collins, JA}
\newcommand{\behn}{Behn, MD}
\newcommand{\RobE}{Evans, RL}
\newcommand{\Walid}{Ben Mansour, W}
\newcommand{\Doug}{Wiens, DA}
\newcommand{\Russo}{Russo, RM}
\newcommand{\ARich}{Richter, A}
\newcommand{\EMard}{Marderwald, E}
\newcommand{\Rodrigo}{Adaros, R}
\newcommand{\SBarr}{Barrientos, S}
\newcommand{\Ivins}{Ivins, ER}
\newcommand{\Bix}{Magnani, MB}
\newcommand{\Billy}{Shinevar, WJ}
\newcommand{\Fiona}{Clerc, F}
\newcommand{\Emman}{Codillo, EA}
\newcommand{\Jianhua}{Gong, J}
\newcommand{\jao}{Olive, JA}
\newcommand{\SBrow}{Brown, SM}
\newcommand{\PSmal}{Smalls, PT}
\newcommand{\Yang}{Liao, Y}
\newcommand{\Vero}{Le Roux, V}
\newcommand{\Nate}{Miller, NC}
\newcommand{\Yajing}{Liu, Y}
\newcommand{\Donna}{Shillington, D}
\newcommand{\Ari}{Cortes Rivas, V}
\newcommand{\JEst}{Estep, JD}
\newcommand{\Patrickelder}{Shore, P}
\newcommand{\Maeva}{Pourpoint, M}
\newcommand{\PLin}{Lin, PP}
\newcommand{\ESar}{Sarafian, EK}
\newcommand{\ZMa}{Ma, Z}
\newcommand{\CDal}{Dalton, CA}
\newcommand{\Dion}{Heinz, DL}
\newcommand{\Masako}{Tominaga, M}
\newcommand{\WSage}{Sager, W}
\newcommand{\CRowe}{Rowe, C}
\newcommand{\MAgi}{Agius, M}
\newcommand{\JConv}{Convers, J}
\newcommand{\GFun}{Funning, G}
\newcommand{\CGal}{Galasso, C}
\newcommand{\SHic}{Hicks, S}
\newcommand{\THuy}{Huynh, T}
\newcommand{\JLan}{Lange, J}
\newcommand{\TLec}{Lecocq, T}
\newcommand{\ROku}{Okuwaki, R}
\newcommand{\Thea}{Ragon, T}
\newcommand{\CRyc}{Rychert, C}
\newcommand{\STep}{Teplitzky, S}
\newcommand{\MvdE}{van den Ende, M}
\newcommand{\EKar}{Karasözen, E}
\newcommand{\RDCF}{Corona-Fernandez, RD}
\newcommand{\Maurice}{Tivey, M}



% Template configuration
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Disable hyphenation
\usepackage[none]{hyphenat}

% Control the font size
\usepackage{anyfontsize}

% Icon fonts (requires using xelatex or luatex)
\usepackage[fixed]{fontawesome5}
\usepackage{academicons}

% Template variables for styling
\newcommand{\TablePad}{\vspace{-0.4cm}}
\newcommand{\SoftwareTitle}[1]{{\bfseries #1}}
\newcommand{\TableTitle}[1]{{\fontsize{12pt}{0}\selectfont \itshape #1}}

% For fancy and multipage tables
\usepackage{tabularx}
\usepackage{ltablex}

% Define a new environment to place all CV entries in a 2-column table.
% Left column are the dates, right column the entries.
\usepackage{environ}
\NewEnviron{EntriesTable}{
\TablePad
\begin{tabularx}{\textwidth}{@{}p{0.12\textwidth}@{\hspace{0.02\textwidth}}p{0.86\textwidth}@{}}
  \BODY
\end{tabularx}
}

% Macros to add links and mark publications
\newcommand{\DOI}[1]{doi:\href{https://doi.org/#1}{#1}}
\newcommand{\dataDOI}[2]{\href{https://doi.org/#2}{#1}}
\newcommand{\DOILink}[1]{\href{https://doi.org/#1}{doi.org/#1}}
\newcommand{\Website}[1]{\href{https://#1}{#1}}
\newcommand{\Preprint}[1]{\newline Preprint: \faFilePdf\ \DOILink{#1}}
\newcommand{\Youtube}[1]{\newline Recording: \faYoutube\, \href{https://www.youtube.com/watch?v=#1}{youtube.com/watch?v=#1}}
\newcommand{\GitHub}[1]{\faGithub\ \href{https://github.com/#1}{github.com/#1}}
\newcommand{\Role}[1]{\newline Role: \faUsers\ #1}
\newcommand{\Slides}[1]{\newline Slides: \faTv\ \href{https://#1}{#1}}
\newcommand{\SlidesDOI}[1]{\newline Slides: \faTv\ \DOILink{#1}}
\newcommand{\PosterDOI}[1]{\newline Poster: \faImage\ \DOILink{#1}}
\newcommand{\OA}{\aiOpenAccess}

% Macros to set the year and duration on the left column
\newcommand{\Duration}[2]{\fontsize{9pt}{0}\selectfont #1 -- #2}
\newcommand{\Year}[1]{\fontsize{9pt}{0}\selectfont #1}
\newcommand{\Ongoing}{on}  % or use 'on'?
\newcommand{\Future}{future}
\newcommand{\Appointment}[4]{\textbf{#1} \newline #2 \newline #3 \newline #4}

% Define command to insert month name and year as date
\usepackage{datetime}
\newdateformat{monthyear}{\monthname[\THEMONTH], \THEYEAR}

% Set the page margins
\usepackage[letterpaper,margin=1in,includehead,headsep=5mm]{geometry}

% To get the total page numbers (\pageref{LastPage})
\usepackage{lastpage}

% No indentation
\setlength\parindent{0cm}

% Increase the line spacing
\renewcommand{\baselinestretch}{1.2}
% and the spacing between rows in tables
\renewcommand{\arraystretch}{1.2}

% Remove space between items in itemize and enumerate
\usepackage{enumitem}
\setlist{nosep}

% Use custom colors
\usepackage[usenames,dvipsnames]{xcolor}

% Set fonts (requires compilation with xelatex)
\usepackage{fontspec}
\setmainfont[%
  Path = fonts/notoserif/,
  UprightFont = NotoSerif-Regular,
  BoldFont = NotoSerif-Bold,
  ItalicFont = NotoSerif-Italic,
  Extension = .ttf
]{NotoSerif}

% Set the spacing for sections
\usepackage{titlesec}
\titleformat{\section}
  {\normalfont\large\mdseries} % format
  {} % label
  {0pt} % separation (left separation for hang)
  {} % text before title
  [\titlerule] % text after title
\titleformat{\subsection}
  {\normalfont\mdseries} % format
  {} % label
  {0pt} % separation (left separation for hang)
  {} % text before title

% Disable number of sections. Use this instead of "section*" so that the sections still
% appear as PDF bookmarks. Otherwise, would have to add the table of contents entries
% manually.
\makeatletter
\renewcommand{\@seccntformat}[1]{}
\makeatother

% Set fancy headers
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
%\lhead{\fontsize{9pt}{10pt}\selectfont
%  \monthyear\today
%}
%\chead{
%  \fontsize{9pt}{10pt}\selectfont
%  \MyName
%  \hspace{0.2cm} -- \hspace{0.2cm}
%  \Title
%}
%\rhead{\fontsize{9pt}{10pt}\selectfont \thepage{} of \pageref*{LastPage}}
\renewcommand{\headrulewidth}{0pt}

% Metadata for the PDF output and control of hyperlinks
\usepackage[colorlinks=true]{hyperref}
\hypersetup{
  pdftitle={\MyName\ - \Title},
  pdfauthor={\MyName},
  linkcolor=blue,
  citecolor=blue,
  filecolor=black,
  urlcolor=MidnightBlue
}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% No header for the first page
\thispagestyle{empty}

% Remove extra header space
\vspace*{-2.75\baselineskip}

\begin{minipage}[t]{0.6\textwidth}
  {\fontsize{16pt}{0}\selectfont\MyName}
\end{minipage}
\begin{minipage}[t]{0.4\textwidth}
  \begin{flushright}
    Last updated: \monthyear\today
  \end{flushright}
\end{minipage}
\\[-0.1cm]
\rule{\textwidth}{1pt}
\vspace{-0.75cm}
\begin{center}
  Email: \href{mailto:\Email}{\Email} |
  ORCID: \href{https://orcid.org/\ORCID}{\ORCID} |
  Website: \Website{\PersonalWebsite}
  \\
  \Address
\end{center}
\vspace{-0.5cm}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Education}

\begin{EntriesTable}
  \Year{2019}  &
  \textbf{PhD in Marine Geophysics}, \JP
  \\
  \Year{2014}  &
  \textbf{BA Physics, BS Geophysical Sciences}, \UChi
\end{EntriesTable}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Professional Appointments}

\begin{EntriesTable}
  \Duration{2025}{\Ongoing}  &
  \textbf{Lamont Assistant Research Professor}, \LDEO, \CU
  \\
  \Duration{2025}{\Ongoing}  &
  \textbf{Adjunct Scientist}, \WHOI
  \\
  \Duration{2025}{2025}  &
  \textbf{Research Associate 3}, \WHOI
  \\
  \Duration{2021}{2025}  &
  \textbf{Postdoctoral Investigator}, \WHOI
  \\
  \Duration{2019}{2021}  &
  \textbf{Fossett Postdoctoral Fellow}, \WUSTL
%  \\
%  \Year{2013}  &
%  \textbf{Summer Student Fellow}, \WHOI
%  \\
%  \Duration{2011}{2014}  &
%  \textbf{Undergraduate Research Assistant}, \UChi
\end{EntriesTable}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Publications}

\begin{EntriesTable}
\Year{2024}  &
  \Me.
  Refining the extent and depth of the shear zone surrounding the Alpine Fault using receiver function harmonics.
  \emph{Geophysical Research Letters.}
  \DOI{10.1029/2024GL112092} \newline
  Preprint \href{https://doi.org/10.22541/essoar.172434288.86649219/v1}{available on essoar}
  \\
\Year{2024}  &
  \Me, Zhu, J, \Masako, Aliod, D, \Maurice.
  shipgrav: A Python package for marine gravimetry.
  \emph{Journal of Open Source Software.}
  \DOI{10.21105/joss.07358} \newline
  Open code: \href{https://github.com/PFPE/shipgrav}{github repository}, \href{https://shipgrav.readthedocs.io}{documentation}, and \dataDOI{archive of v1.0.6}{10.5281/zenodo.14199589}
  \\
\Year{2024}  &
  Gourdeau, A, Prush, VB, \CRowe, Nackers, C, \Me, Morris, I, Rosset, P, Lamothe, M, Chouinard, L, Tarling, MS.
  Investigation of suspected Holocene fault scarp near Montr\`{e}al, Qu\`{e}bec: The first paleoseismic trench in eastern Canada.
  \emph{Seismica.}
  \DOI{10.26443/seismica.v3i2.1179}
  \\
\Year{2023}  &
  \Me, \danl, \Doug.
  Constraints on bend-faulting and mantle hydration at the Marianas Trench from seismic anisotropy.
  \emph{Geophysical Research Letters.}
  \DOI{10.1029/2023GL103331} \newline
  Open data: \dataDOI{scripts for anisotropy calculations}{10.5281/ZENODO.7105231}
  \\
\Year{2022}  &
  \Josh, \Jim, \Me, \Greg, \LHans, \danl, \jac, \RobE. 
  Seismological evidence for girdled olivine lattice-preferred orientation in oceanic lithosphere and implcations for mantle deformation processes during seafloor spreading. 
  \emph{Geochemistry, Geophysics, Geosystems.}
  \DOI{10.1029/2022GC010542}
  \\
\Year{2022}  &
  \Walid, \Doug, \Me, \Russo, \ARich, \EMard, \SBarr. 
  Mantle flow pattern associated with the Patagonian slab window determined from azimuthal anisotropy. 
  \emph{Geophysical Research Letters.}
  \DOI{10.1029/2022GL099871}
  \\
\Year{2022}  &
  \Me, \Doug, \Ivins, \ARich, \Walid, \Bix, \EMard, \Rodrigo, \SBarr.
  Lithospheric erosion in the Patagonian slab window, and implications for glacial isostasy.
  \emph{Geophysical Research Letters.}
  \DOI{10.1029/2021GL096863} \newline
  Open data: \dataDOI{velocity and viscosity models}{10.5281/zenodo.5794167}, and some \dataDOI{cross-correlations}{10.5281/zenodo.5508198}
  \\
\Year{2021}  &
  \Me, \jac, \danl, \Greg, \Jim, \RobE, \behn.
  Constraints on the depth, thickness, and strength of the G discontinuity in the central Pacific from S receiver functions.
  \emph{Journal of Geophysical Research: Solid Earth.}
  \DOI{10.1029/2019JB019256}
  \\
\Year{2019}  &
  \Billy, \Me, \Fiona, \Emman, \Jianhua, \jao, \SBrow, \PSmal, \Yang, \Vero, \behn.
  Causes of oceanic crustal thickness oscillations along a 74-Myr Mid-Atlantic Ridge flow line.
  \emph{Geochemistry, Geophysics, Geosystems.}
  \DOI{10.1029/2019GC008711}
  \\
\Year{2019}  &
  \Me, \danl, \jac, \Nate, \Greg, \Jim, \RobE.
  Azimuthal seismic anisotropy of 70 Ma Pacific-plate upper mantle. 
  \emph{Journal of Geophysical Research: Solid Earth.}
  \DOI{10.1029/2018JB016451}
  \\
\Year{2018}  &
  \Me, \behn, \jao, \Yajing.
  Controls on Mid-ocean Ridge Normal Fault Seismicity Across Spreading Rates From Rate-and-State Friction Models 
  \emph{Journal of Geophysical Research: Solid Earth.}
  \DOI{10.1029/2018JB015545}
  \\
\end{EntriesTable}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Manuscripts in progress}

\begin{EntriesTable}
\Year{In revision}  &
  \Me, \Doug, \Walid, Zhou, Z.
  Depth-varying azimuthal anisotropy and mantle flow in the Patagonian slab window.
  \small\emph{Copies available on request}.
  \\
\Year{In prep}  &
  \Me, \danl, \Donna, \Ari, \behn.
  Along-strike seismic structure of the Andreanof Aleutian Arc Segment, with implications for the formation of continental crust.
  \small\emph{Copies available on request}.
\end{EntriesTable}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Reviewed editorials}

\begin{EntriesTable}
\Year{2023}  &
  \Me, \Thea, \GFun, \SHic, \CRowe, \STep, \JConv, \EKar, \RDCF.
  Editorial workflow of a community-led, all-volunteer scientific journal: lessons from the launch of Seismica.
  \emph{Seismica.}
  \DOI{10.26443/seismica.v2i2.1091} \\
\Year{2022}  &
  \CRowe, \MAgi, \JConv, \GFun, \CGal, \SHic, \THuy, \JLan, \TLec, \Me, \ROku, \Thea, \CRyc, \STep, \MvdE. 
  The launch of Seismica: a seismic shift in publishing. 
  \emph{Seismica.}
  \DOI{10.26443/seismica.v1i1.255}
\end{EntriesTable}





%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Funding}

\begin{EntriesTable}
  \Duration{2023}{2024}  &
  NSF-OCE: ``An assessment of low-temperature, ductile lithospheric deformation using existing broadband seismic data from around South Island, New Zealand''. \newline
  Award ID: \href{https://www.nsf.gov/awardsearch/showAward?AWD_ID=2316757}{2316757}.
  PI: \Me. \newline
  \small \$84k to HF Mark
  \\
  \Duration{2023}{2025}  &
  NSF-OCE: ``Collaborative Research: Resolving the Origin of the Jurassic Quiet Zone''. \newline
  Award ID: \href{https://www.nsf.gov/awardsearch/showAward?AWD_ID=2221814}{2221814}.
  PI: \Masako, co-PIs: \Me; \WSage. \newline
  \small \$827k to WHOI including \$192k to HF Mark
  %\\
\end{EntriesTable}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Awards}

\begin{EntriesTable}
  \Year{2023} & \textbf{Seismica Moment Award}, Seismica journal
  \\
  \Year{2019} & \textbf{Fossett Postdoctoral Fellowship}, \WUSTL
  \\
  \Year{2019} & \textbf{AGU Outstanding Student Paper Award (OSPA)}, Tectonophysics
  \\
  \Year{2016} & \textbf{AGU OSPA}, Tectonophysics
  \\
  \Year{2016} & \textbf{GeoPrisms OSPA}, honorable mention
  \\
  \Year{2015} & \textbf{National Science Foundation Graduate Research Fellowship}
  \\
  \Year{2014} & \textbf{Rosenblith Presidential Fellowship}, \MIT
  \\
  \Year{2014} & \textbf{Phi Beta Kappa}, Beta of Illinois
  \\
  \Year{2013} & \textbf{John Crerar Science Writing Prize}, \UChi
\end{EntriesTable}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Teaching Experience}

\begin{EntriesTable}
  \Year{2025} & \textbf{Buzzards Bay Term}, \gull, Natural science faculty
  \\
  \Year{2024} & \textbf{Buzzards Bay Term}, \gull, Natural science faculty
  \\
  \Year{2023} &
  \textbf{WHOI Software Carpentries Python workshop}, Course assistant
  \\
  \Year{2020} &
  \textbf{EPS 564: Multidisciplinary Study of Subduction Zones}, \WUSTL, Guest lecturer
  \\
  \Year{2018} &
  \textbf{Kaufman Teaching Certificate}, MIT Teaching and Learning Lab
  \\
  \Year{2018} &
  \textbf{WHOI Software Carpentries git workshop}, Course assistant
  \\
  \Year{2017} &
  \textbf{MS-3221: Oceanography}, Massachusetts Maritime Academy, Co-Instructor
  \\
  \Year{2016} &
  \textbf{12.710: Elements of Modern Oceanography}, \JP, TA
  \\
  \Year{2016--2017} &
  \textbf{\mathrev}, Lecturer
\end{EntriesTable}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Academic Service}

\begin{EntriesTable}
  \Duration{2022}{\Ongoing} & \href{https://seismica.library.mcgill.ca}{\textbf{\textit{Seismica}}} journal management committee, Co-chair of Standards and Copy Editing
  \\
  \Duration{2022}{2024} & \textbf{WHOI Postdoc Association}, Department representative
  \\
  \Duration{2022}{2024} & \textbf{WHOI Workplace Climate Committee}, Postdoc representative
  \\
  \Duration{2022}{2023} & \textbf{WHOI G\&G Proposal Club}, Co-organizer
  \\
  \Year{2021} & \textbf{WUSTL EPS Department URGE pod}, Pod leader
  \\
  \Duration{2018}{2019} & \textbf{500 Women Scientists of Cape Cod}, Steering Committee member
  \\
  \Duration{2015}{2019} & \textbf{\JP\ Farrington Collection}, Librarian
   \\
  \Duration{2014}{2016} & \textbf{\mathrev}, Coordinator
  \\
  ~ & \textbf{Peer reviewer for:} JGR Solid Earth, Nature Geoscience, Geophysical Research Letters, Science Advances, Nature Communications, Journal of Open Source Software, Geoscience Letters, Earth and Planetary Science Letters, Seismological Research Letters, Geological Society of London Special Publications, Seismica, Tectonics, The Seismic Record, Canadian Journal of Earth Sciences, Geophysical Journal International
  \\
  ~ & \textbf{Conference sessions convened:} SSA Annual Meeting 2022, \textit{Marine Seismology}; AGU Fall Meeting 2021, \textit{EP15 -- Coupling of the Cryosphere, Solid Earth, Surface, and Climate in Shaping Late Cenozoic Topography}
\end{EntriesTable}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Workshops and short courses}

\begin{EntriesTable}
\Year{2022} & IRIS Magnetotelluric Instrumentation and Data Processing Short Course  \\
\Year{2017} & WHOI Communications Course -- How NOT to write for peer-reviewed journals: Talking to everyone else \\
\Year{2017} & MBL Writing about Science for the Public workshop \\
\Year{2015} & WHOI Ocean Law and Policy Seminar
\end{EntriesTable}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Invited Seminars}

\begin{EntriesTable}
\Year{2024}  & \textbf{Lamont Doherty Earth Observatory}, MPG/SGT Department seminar
  \\
 ~  & \textbf{Texas A\&M University}, Oceanography Department seminar
  \\
\Year{2023}  & \textbf{McGill University}, EPS Department seminar
  \\
  ~ & \textbf{University of Arizona}, Geosciences Colloquium
  \\
\Year{2022}  & \textbf{University of Washington School of Oceanography}
  \\
  ~ & \textbf{University of Wisconsin Madison}, Weeks Seminar
  \\
  ~ & \textbf{Syracuse University}, EES Department Colloquium
  \\
\Year{2021} & \textbf{University of Hawai'i Manoa}, Earth Sciences Department seminar
  \\
\Year{2019} & \textbf{University of Illinois Urbana-Champaign}, Brown bag seminar
  \\
\Year{2018} & \textbf{Lamont-Doherty Earth Observatory}, MGG/SGT seminar
  \\
  ~ & \textbf{WHOI}, Interdisciplinary Biology Seminar Series on Acoustics
\end{EntriesTable}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Field Experience}

\begin{EntriesTable}
  \Year{2024} & R/V \textit{Sikuliaq}, SKQ202418S. \newline
  \small MCS and magnetic survey in the western Pacific (chief sci).
  \\
  \Year{2020} & R/V \textit{Marcus G. Langseth}, MGL2003. \newline
  \small Active-source reflection and refraction survey in the Central Aleutians
  \\
  \Year{2017} & R/V \textit{Neil Armstrong}, AR23-02. \newline
  \small Collecting underway data along a ridge flowline in the Atlantic
  \\
  \Year{2016} & R/V \textit{Neil Armstrong}, AR05. \newline
  \small Scientific validation cruise
  \\
  \Year{2015} & ENAM land seismic experiment, North Carolina. \newline
  \small RT-125 deployment and recovery for active-source seismic lines on the Eastern North American Margin
  \\
  \Year{2014} & PRIDE SeisORZ seismic experiment, Botswana. \newline
  \small RT-125 deployment and recovery for an active-source seismic line across the Okavango Delta
  \\
\end{EntriesTable}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Selected Communication and Outreach}

\begin{EntriesTable}
  \Duration{2023}{on} & Essay reviewer for \href{https://www.sye-initiative.org}{Syrian Youth Empowerment Initiative}.
  \\
  \Year{2021} & Panel speaker for virtual AGU event on "Submitting your first paper"
  \\
  \Duration{2020}{2022} & Contributing writer and peer editor at \Website{geobites.org} \newline
  \small Blogging, general audience summaries of new research
  \\
  \Year{2018} & \href{https://www.whoi.edu/oceanus/feature/hannah-mark/}{How is the seafloor made?} \newline
  \small Magazine article, \textit{Oceanus} Vol 53. No. 2
  \\
  \Year{2017} & (Way) under the sea: Imaging the rocks beneath the deep ocean \newline
  \small Public talk, Science Made Public lecture series, Woods Hole, MA
  \\
  ~ & The lithosphere-asthenosphere boundary: What it is, where it is, and why you should care \newline
  \small Public talk, Woods Hole Public Library, Woods Hole, MA
  \\
  \Year{2016} & Under-under the sea: Imaging the rocks beneath the deep ocean \newline
  \small Public talk, Woods Hole Public Library, Woods Hole, MA
  \\
\end{EntriesTable}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conference Abstracts \small (*=invited)}
\begin{EntriesTable}
\Year{2024} & 
    \Me.
    \textit{Estimating the Extent of Low-temperature Ductile Deformation in the Lithosphere Using Seismic Anisotropy Measurements Around the Alpine Fault.}
    SSA Annual Meeting, Anchorage, AK. \\
 ~ &
    \Me, \danl, \Donna, \Ari.
    \textit{Seismic Structure of Arc Crust in the Andreanof Segment of the Aleutian Arc from Wide-angle Refraction Data.}
    SSA Annual Meeting, Anchorage, AK. \\
~ & *\Me. 
    \textit{Open Science for geoscience workshop.} ACCESS, Tempe, AZ. \\
\Year{2023} &
  Gourdeau, A, Prush, V, \CRowe, Wang, K, Rosset, P, Chouinard, L, Lamothe, M, \Me, Morris, I, Laly, M, Nackers, C.
  \textit{An Ongoing Search for Active Faults in the Western Quebec Seismic Zone, Eastern Canada.}
  \AGU, San Francisco, CA. \\
\Year{2022} &
  *\Me, \jac, \danl, \Jim, \Greg, \RobE, \behn.
  \textit{Where is the G discontinuity, what does it represent, and how can we tell? A case study from the NoMelt experiment.}
  \AGU, Chicago, IL.
  \\
  ~ &
  \Ari, \Donna, \danl, \Me, \JEst, Boston, B.
  \textit{Seismic reflection imaging of along-strike changes in forearc structure in the Andreanof segment of the Aleutian subduction zone.}
  \AGU, Chicago, IL.
  \\
  ~ &
  \Josh, \Jim, \Me, \Greg, \LHans, \danl, \jac, \RobE.
  \textit{Seismological Evidence for Girdled Olivine Fabric in Oceanic Lithosphere and Implications for Mantle Deformation Processes During Seafloor Spreading.}
  \AGU, Chicago, IL.
  \\
  ~ &
  \Doug, \Walid, \Me.
  \textit{Seismic Anisotropy and Mantle Dynamics Associated with Slab Windows.}
  \AGU, Chicago, IL.
  \\
  ~ &
  \Me, \Doug, \danl.
  \textit{Insights into bend-faulting and mantle hydration at the Marianas trench from seismic anisotropy.}
  SSA Annual Meeting, Belleview, WA (poster).
  \\
\Year{2021} &
  \Me, \Doug, \Walid, \Ivins, \ARich, \Bix, \EMard, \Rodrigo, \SBarr.
  \textit{Thermal erosion of the lithosphere in the Patagonian slab window and implications for glacial isostatic adjustment.}
  \AGU, New Orleans, LA.
  \\
  ~ &
  \Me, \danl, \Donna, \Ari, \JEst.
  \textit{Crustal structure along-strike in the Andreanof segment of the Aleutian Arc from wide-angle seismic refraction data.}
  \AGU, virtual (poster).
  \\
  ~ &
  \Doug, \Walid, \Me, \Patrickelder, \ARich, \SBarr.
  \textit{Geodynamics of the Patagonian Slab Window Constrained by Shear Wave Splitting and Seismic Imaging.}
  \AGU, New Orleans, LA.
  \\
  ~ &
  \Me, \Doug, \danl.
  \textit{Estimating bend-faulting and mantle hydration at the Marianas trench from seismic anisotropy.}
  EGU General Assembly, virtual.
  \\
  ~ &
  *\Me.
  \textit{Anisotropy in slightly more than one dimension.}
  Marine Seismology Symposium, virtual.
  \\
  ~ &
  \Me, \Doug, \danl.
  \textit{Estimating bend-faulting and mantle hydration at the Marianas trench from seismic anisotropy.}
  Marine Seismology Symposium, virtual (poster).
  \\
\Year{2020} & 
  \Me, \Doug, \Maeva, \Bix, \Ivins, \ARich, \SBarr.
  \textit{Seismic structure and the extent of the slab window beneath the Northern and Southern Patagonian Icefields.}
  \AGU, virtual (poster).
  \\
\Year{2019} &
  \Me, \jac, \danl, \Greg, \Jim, \RobE.
  \textit{The depth, sharpness, and strength of the G discontinuity from S-to-p receiver functions at the NoMelt site in the central Pacific.}
  \AGU, San Francisco, CA.
  \\
\Year{2018} &
  \Me, \jac, \danl, \Greg, \Jim, \RobE.
  \textit{S-to-p receiver functions for the central Pacific from NoMelt.}
  \AGU, Washington, D. C.
  \\
  ~ &
  \Billy, \Me, \Fiona, \Emman, \jao, \Jianhua, \SBrow, \PSmal, \Yang, \Vero, \behn.
  \textit{Temporal variability of seafloor spreading processes documented along an 80-Myr geophysical transect across the Mid-Atlantic Ridge.}
  \AGU, Washington, D.C.
  \\
  ~ &
  \Jim, \Josh, \Me, \PLin, \ESar, \ZMa, \danl, \jac, \Greg, \RobE, \CDal.
  \textit{A comprehensive portrait of the central Pacific lithosphere-asthenosphere system from NoMelt seafloor geophysical observations.}
  \AGU, Washington, D.C.
  \\
\Year{2017} &
  *\Me, \behn, \Yajing, \jao.
  \textit{Geometric and thermal controls on normal fault seismicity.}
  \AGU, New Orleans, LA.
  \\
  ~ &
  \Me, \danl, \jac, \Nate, \Greg, \Jim, \RobE.
  \textit{Seismic anisotropy of 70 Ma Pacific-plate upper mantle.}
  \AGU, New Orleans, LA.
  \\
  ~ &
  *\Me, \behn, \Yajing, \jao.
  \textit{Seismic coupling at divergent plate boundaries from rate-and-state friction.}
  GeoPrisms TEI on Rift Initiation and Evolution, Albuquerque, NM.
  \\
\Year{2016} &
  \Me, \behn, \Yajing, \jao.
  \textit{Seismic coupling at divergent plate boundaries from rate-and-state friction.}
  \AGU, San Francisco, CA.
  \\
  ~ &
  \Me, \behn, \Yajing, \jao.
  \textit{Rate-and-state friction models of seismic cycles on oceanic normal faults.}
  GRC on Rock Deformation, Andover, NH (poster).
  \\
  ~ &
  \Me, \danl, \Jim, \jac, \Greg, \RobE, \PLin.
  \textit{Seismic anisotropy in the Pacific upper mantle.}
  Seismology Student Workshop, Lamont Doherty Earth Observatory.
  \\
\Year{2014} &
  \Me, \danl, \Jim, \jac, \Greg, \RobE.
  \textit{Pacific upper mantle seismic anisotropy from the active-source component of the NoMelt experiment.}
  \AGU, San Francisco, CA (poster).
  \\
\Year{2012} &
  \Dion, \Me.
  \textit{The Effect of Wavelength-Dependent Emissivity on the Melting Temperature of Iron from Shock Wave Measurements.}
  \AGU, San Francisco, CA (poster).
\end{EntriesTable}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\section{Open Science}
%
%\begin{EntriesTable}
%  \Duration{2010}{\Ongoing} &
%  \textbf{Fatiando a Terra} | \Website{www.fatiando.org}
%  \newline
%  Python tools for geophysical data processing, forward modeling, and inversion
%  \\
%  \Duration{2017}{\Ongoing} &
%  \textbf{PyGMT} | \Website{www.pygmt.org}
%  \newline
%  A Python interface for the Generic Mapping Tools
%  \\
%  \Duration{2017}{\Ongoing} &
%  \textbf{The Generic Mapping Tools (GMT)} | \Website{www.generic-mapping-tools.org}
%  \newline
%  A data processing and mapping toolbox for the Earth, Ocean, and Planetary Science
%  \\
%  \Duration{2009}{2016} &
%  \textbf{Tesseroids} | \Website{tesseroids.leouieda.com}
%  \newline
%  Forward modeling of gravitational fields in spherical coordinates
%\end{EntriesTable}


\end{document}


